Parametrization of Invertible Resnets up to Homology Equivalence for Connected Abelian Lie Groups

### 2020-04-04 llncs2e/paper77.tex
lekyRelu

\paragraph{Neural Nets} The data manifold is supposed to be some connected commutative Lie group. We perturb each input vector $\textbf{x}^{(0)}$ with Gaussian noise, such that the input is weighted $0.8 \cdot \textbf{x}^{(0)} + 0.5 \cdot \epsilon$ with $\epsilon \sim \mathcal{N}(0,\sigma^2 \mathbf{I})$. These input vectors are trained to the original vector $\textbf{x}^{(0)}$. We use $\text{L}(\textbf{x}^{(0)}, \textbf{y}) = \frac{1}{n} \sum_{i=1}^{n} \left(\textbf{x}^{(0)}_i-\textbf{y}_i\right)^2$ as loss function. The sigmoid activation function $\sigma(\mathbf{x}^{(l)}) = \frac{1}{1 + e^{-\mathbf{x}^{(l)}}}$ is applied as elementwise activation function throughout the net. In all experiments dense neural nets are used with a bias term. The datasets are flattened from $(32,32,3)$ into $(3072)$. The first layer is applied to the flattened dataset, which is also adapted by back propagation, i.e. $\varphi^{(0)}\left(x^{(0)} \right) =$ $\sigma\left( \sum_{i=1}^{n} \textbf{W}_{ji}^{(1)} \textbf{x}_{i}^{(0)} + \textbf{b}_{i}^{(1)} \right)$. It transfers the data to the desired embedding dimension. The subsequent layers are implemented as $\mathcal{C}^1$-residual invertible layers, see Sect. \ref{resnet} and Sect. \ref{subsec:invertibleneuralnets}. A total of $5$ of these hidden layers are used, all with the same embedding dimension. More details can be found in Appx. \ref{appx:numexp}.

@@

\subsubsection{Invertible $\mathcal{C}^1$-Net}
\label{appx:invarch}
The neural net used in Sect. \ref{sec:numericalexperiments} is a partially invertible architecture. It consists of a total of five hidden layers. The first layer is a dense layer, which connects the input $\mathbf{x}^{(0)} \mapsto \text{BN}\left(\sigma\left(\sum_{i=1}^{n} \textbf{W}^{(1)}_{ji}\mathbf{x}^{(0)}_{i} + \mathbf{b}^{(1)}_{i}\right)\right)$ to a subspace of $\mathbf{x}^{(0)} \in \mathbb{R}^n$. The subspace is initially $\mathbb{R}^{n-k}$ with $(n-k) \leq n$, according to Fig. \ref{architecture}. The sigmoid function is used as activation function. The weights are initialized uniformly distributed and the bias term is with zeros, respectively. The batch normalization can be expressed for a batch $k$ at the $l$-th layer as
\begin{align}
	\text{BN}(\mathbf{x}^{(l)}_{(k)})_{\gamma^{(l)}_{(k)},\beta^{(l)}_{(k)}} = \frac{\gamma}{\sqrt{\text{Var}[\mathbf{x}^{(l)}_{(k)}] + \epsilon}} \mathbf{x}^{(l)}_{(k)} + \left( \beta - \frac{\gamma \text{E}[\mathbf{x}^{(l)}_{(k)}]}{\sqrt{\text{Var}[\mathbf{x}^{(l)}_{(k)}]+\epsilon}} \right),
\end{align}
where $\gamma,\beta$ and $\epsilon$ are parameters updated during back propagation. The very first and last dense layer is not invertible. Its purpose is a learned projection into the desired subspace of dimension $(n-k)$ for some $k$ and afterwards projecting into the original space in an encoding fashion, see Fig. \ref{architecture}.

\subsubsection{Non-invertible $\xi_i$- and $\psi_i$-Architecture}
The invertible architecture, which is described in Sect. \ref{subsec:invertibleneuralnets}, uses the partially linear functions $\xi_1,\xi_2$ and $\psi_1,\psi_2$, which are parameterized during the learning process. The architecture is taken from the work of Ardizzone et al. \cite{ArdizzoneKRK19}. These functions are to be learned and are composed in a trivially invertible way, see Sect. \ref{subsec:invertibleneuralnets}. The functions themselves are implemented as neural subnets. Each function is a $\mathcal{C}^1$-net with a total of $3$ dense layers, see Sect. \ref{resnet}. The vector $\mathbf{u}_{1}^{(l)} \in \text{M}(n,\mathbb{R})$ is transformed by $\xi_1,\xi_2,\psi_1,\psi_2: \text{M}(n,\mathbb{R}) \rightarrow \text{M}(n,\mathbb{R})$, such that the dimension of the vector does not change. The leaky rectifying linear unit activation function has been selected for every layer in the subnet:
\begin{align}
	\text{LeakyReLu}(\mathbf{x}^{(l)}) = 
	\begin{dcases}
	    \mathbf{x}^{(l)}_{i},
	    & \text{if} \; \mathbf{x}^{(l)}_{i} \geq 0, \\
	    5.5 \cdot \mathbf{x}^{(l)}_{i}
	    & \text{if} \; \mathbf{x}^{(l)}_{i} < 0.
	\end{dcases}
\end{align}
We apply batch normalization after the activation function, see Appx. \ref{appx:invarch}. The partition of the vector is still an open research question \cite{ArdizzoneKRK19}. We divide the flattened vector precisly into two halfs, since the samples are square matrices:
\begin{align}
\mathbf{x}^{(l)} = (\mathbf{u}^{(l)}_1, 0, \cdots, 0) + (0, \cdots, 0, \mathbf{u}^{(l)}_2).
\end{align}

>>>>

\paragraph{Neural Nets} The data manifold is supposed to be some connected commutative Lie group. We perturb each input vector $\textbf{x}^{(0)}$ with Gaussian noise, such that the input is weighted $0.8 \cdot \textbf{x}^{(0)} + 0.5 \cdot \epsilon$ with $\epsilon \sim \mathcal{N}(0,\sigma^2 \mathbf{I})$. These input vectors are trained to the original vector $\textbf{x}^{(0)}$. We use $\text{L}(\textbf{x}^{(0)}, \textbf{y}) = \frac{1}{n} \sum_{i=1}^{n} \left(\textbf{x}^{(0)}_i-\textbf{y}_i\right)^2$ as loss function. The leaky ReLu Eq. \ref{LeakyReLu} activation function $\sigma(\mathbf{x}^{(l)}) = \frac{1}{1 + e^{-\mathbf{x}^{(l)}}}$ is applied as elementwise activation function throughout the net. In all experiments dense neural nets are used with a bias term. The datasets are flattened from $(32,32,3)$ into $(3072)$. The first layer is applied to the flattened dataset, which is also adapted by back propagation, i.e. $\varphi^{(0)}\left(x^{(0)} \right) =$ $\sigma\left( \sum_{i=1}^{n} \textbf{W}_{ji}^{(1)} \textbf{x}_{i}^{(0)} + \textbf{b}_{i}^{(1)} \right)$. It transfers the data to the desired embedding dimension. The subsequent layers are implemented as $\mathcal{C}^1$-residual invertible layers, see Sect. \ref{resnet} and Sect. \ref{subsec:invertibleneuralnets}. A total of $5$ of these hidden layers are used, all with the same embedding dimension. More details can be found in Appx. \ref{appx:numexp}.

@@

\subsubsection{Invertible $\mathcal{C}^1$-Net}
\label{appx:invarch}
The neural net used in Sect. \ref{sec:numericalexperiments} is a partially invertible architecture. It consists of a total of five hidden layers. The first layer is a dense layer, which connects the input $\mathbf{x}^{(0)} \mapsto \text{BN}\left(\sigma\left(\sum_{i=1}^{n} \textbf{W}^{(1)}_{ji}\mathbf{x}^{(0)}_{i} + \mathbf{b}^{(1)}_{i}\right)\right)$ to a subspace of $\mathbf{x}^{(0)} \in \mathbb{R}^n$. The subspace is initially $\mathbb{R}^{n-k}$ with $(n-k) \leq n$, according to Fig. \ref{architecture}. The leaky ReLu function is used as activation function. The weights are initialized uniformly distributed and the bias term is with zeros, respectively. The batch normalization can be expressed for a batch $k$ at the $l$-th layer as
\begin{align}
	\text{BN}(\mathbf{x}^{(l)}_{(k)})_{\gamma^{(l)}_{(k)},\beta^{(l)}_{(k)}} = \frac{\gamma}{\sqrt{\text{Var}[\mathbf{x}^{(l)}_{(k)}] + \epsilon}} \mathbf{x}^{(l)}_{(k)} + \left( \beta - \frac{\gamma \text{E}[\mathbf{x}^{(l)}_{(k)}]}{\sqrt{\text{Var}[\mathbf{x}^{(l)}_{(k)}]+\epsilon}} \right),
\end{align}
where $\gamma,\beta$ and $\epsilon$ are parameters updated during back propagation. The very first and last dense layer is not invertible. Its purpose is a learned projection into the desired subspace of dimension $(n-k)$ for some $k$ and afterwards projecting into the original space in an encoding fashion, see Fig. \ref{architecture}.

\subsubsection{Non-invertible $\xi_i$- and $\psi_i$-Architecture}
The invertible architecture, which is described in Sect. \ref{subsec:invertibleneuralnets}, uses the partially linear functions $\xi_1,\xi_2$ and $\psi_1,\psi_2$, which are parameterized during the learning process. The architecture is taken from the work of Ardizzone et al. \cite{ArdizzoneKRK19}. These functions are to be learned and are composed in a trivially invertible way, see Sect. \ref{subsec:invertibleneuralnets}. The functions themselves are implemented as neural subnets. Each function is a $\mathcal{C}^1$-net with a total of $3$ dense layers, see Sect. \ref{resnet}. The vector $\mathbf{u}_{1}^{(l)} \in \text{M}(n,\mathbb{R})$ is transformed by $\xi_1,\xi_2,\psi_1,\psi_2: \text{M}(n,\mathbb{R}) \rightarrow \text{M}(n,\mathbb{R})$, such that the dimension of the vector does not change. The leaky rectifying linear unit activation function has been selected for every layer in the subnet:
\begin{align}
\label{LeakyReLu}
	\text{LeakyReLu}(\mathbf{x}^{(l)}) = 
	\begin{dcases}
	    \mathbf{x}^{(l)}_{i},
	    & \text{if} \; \mathbf{x}^{(l)}_{i} \geq 0, \\
	    -5.5 \cdot \mathbf{x}^{(l)}_{i}
	    & \text{if} \; \mathbf{x}^{(l)}_{i} < 0.
	\end{dcases}
\end{align}
We apply batch normalization after the activation function, see Appx. \ref{appx:invarch}. The partition of the vector is still an open research question \cite{ArdizzoneKRK19}. We divide the flattened vector precisly into two halfs, since the samples are square matrices:
\begin{align}
\mathbf{x}^{(l)} = (\mathbf{u}^{(l)}_1, 0, \cdots, 0) + (0, \cdots, 0, \mathbf{u}^{(l)}_2).
\end{align}
